# Study area map

```{r}
library(ggplot2)
library(sf)
library(rnaturalearth)
library(dplyr)
library(terra)
library(ggrepel)
library(tidyverse)
library(RStoolbox)
library(terra)
library(raster)
library(basemaps)
library(ggspatial)
library(cowplot)
library(terrainr)
```

## Study area map

This code chunk creates an outline map of countries, names and places the study sites on the map with arrows and labels

```{r}

crs <- "+proj=ortho +lat_0=46.35 +lon_0=-1.9 +x_0=0 +y_0=0 +a=6371000 +b=6371000 +units=m +no_defs"

ctrys50m <- ne_countries(scale = 10, type = "countries", returnclass = "sf") %>%
  dplyr::select(iso_a3, iso_n3, admin)%>%
  st_transform(., crs = 4326)

capitals <- read_csv("data/country-capitals.csv")%>%
  filter(CountryName=="United Kingdom" | 
           CountryName=="France" | 
           CountryName=="Ireland" |
           CountryName=="Portugal" |
           CountryName=="Spain")%>%
  mutate(CapitalLatitude = as.numeric(CapitalLatitude))%>%
  st_as_sf(., coords=c("CapitalLongitude", "CapitalLatitude"), crs=4326)


valencia2b<-terra::rast("data/f168_3b_mapped_utm30n_atm_brdf_mosaic_30m_enmap_subset")

zoom_to <- c(-0.58, 45.72)  # Berlin
zoom_level <- 3.1
lon_span <- 360 / 2^zoom_level
lat_span <- 180 / 2^zoom_level


lon_bounds <- c(zoom_to[1] - lon_span / 2, zoom_to[1] + lon_span / 2)
lat_bounds <- c(zoom_to[2] - lat_span / 2, zoom_to[2] + lat_span / 2)

ctrys50m_cent <- ctrys50m%>%
  st_make_valid()%>%
  st_centroid()%>%
  st_coordinates()

cntry_label <- cbind(ctrys50m, ctrys50m_cent)%>%
  filter(., admin=="United Kingdom" | admin=="France" | 
           admin=="Ireland" |admin=="Portugal" | admin=="Spain") 

cntry_label$X[cntry_label$admin %in% "France"]<- 0.689200
cntry_label$Y[cntry_label$admin %in% "France"]<- 	47.243599



extent_wytham <- terra::rast("data/ang20210716t_mosaic_30m_enmap_subset")%>%
  ext()%>%
  as.polygons

crs(extent_wytham) <- "+proj=utm +zone=30 +datum=WGS84 +units=m +no_defs +type=crs"

extent_wythamWGS<- extent_wytham%>%
  st_as_sf()%>%
  st_transform(., 4326)

extent_wythamWGS_names <- extent_wythamWGS %>%
  st_centroid()%>%
  st_coordinates()%>%
  as_tibble()%>%
#  st_as_sf(., coords=c(x=X, y=Y))%>%
#  st_set_crs(4326)
  mutate(name="Wytham Woods")

extent_valencia <- terra::rast("data/f168_3b_mapped_utm30n_atm_brdf_mosaic_30m_enmap_subset")%>%
  ext()%>%
  as.polygons()

extent_valenciaWGS <- extent_valencia%>%
  st_as_sf()%>%
  st_set_crs(.,32630)%>%
  st_transform(., 4326)%>%
  st_centroid()%>%  
  st_coordinates()%>%
  as_tibble()%>%
  mutate(name="Valencia")


cntry_label$nudge_y <- 0
cntry_label$nudge_y[cntry_label$admin == "United Kingdom"] <- -1

arrows <- 
  tibble(
    y1 = c(49.4, 45.4),
    y2 = c(51.8, 39.6),
    x1 = c(-8, -8),
    x2=c(-1.33, -1.24))

arrows

val_extent <- st_bbox(valencia2b)%>%
  st_as_sfc(st_bbox(.))%>%
  st_transform(., 4326)



main <- ggplot()+
  geom_sf(data = ctrys50m, fill='antiquewhite', color = gray(.5))+ 
  coord_sf(xlim = c(-13, 4), ylim = c(34, 60))+
    xlab("Longitude") + ylab("Latitude")+
    geom_label(data = cntry_label, aes(X, Y, label = admin), size = 2.5,
               nudge_y = cntry_label$nudge_y)+ 
    geom_curve(
      data = arrows, aes(x = x1, y = y1, xend = x2, yend = y2),
      arrow = arrow(length = unit(0.08, "inch")), linewidth = 0.9,
      color = "gray20", curvature = -0.3)+
  annotate("text", x = -8, y = 49, 
           label = "Wytham Woods", size=3, fontface =2)+
  annotate("text", x = -8, y = 46, label = "Valencia Anchor Station", size=3,
           fontface =2)+
  theme_bw()+
  theme(panel.grid.major = element_line(color = gray(0.25), 
                                            linetype = "dashed", 
                                            linewidth = 0), 
            panel.background = element_rect(fill = "aliceblue"))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())

main



```

## OSM maps

Here OSM data is plotted with elementary sampling units (ESUs) and place labels for both Valencia and Wytham.

### Valencia

```{r}
valencia_17 <- read.table("data/valencia17_coordinates.txt",sep="\t",header=T)%>%
  as_tibble()%>%
  st_as_sf(coords = c('Longitude', 'Latitude')) %>%
  st_set_crs(4326)%>%
  st_transform(32630)%>%
  mutate(Year="2017")

sub_valencia<- subset(valencia2b, c(9,23,41))%>%
  subst(., 0, NA)%>%
  crop(., valencia_17)

set_defaults(map_service = "osm", map_type = "streets")

#basemap_magick(all)


places_Spain <- tibble(name = c("Utiel", "Los Corrales"), X = c(-134164.6, -141510), Y = c(4803342.7, 4807143))

# places_Spain <- tibble(name = c("Utiel", "Caudete de las Fuentes", "Los Corrales"), X = c(-134164.6,-142509, -141510), Y = c(4803342.7, 4802270, 4807143))


valencia_17 <- valencia_17 %>%st_transform(., 3857)


valencia_plot <- ggplot()  +
   basemap_gglayer(valencia_17, alpha=0.8)+
    scale_fill_identity() + 
  coord_sf()+
    #ggRGB(sub_valencia, r = 3, g = 2, b = 1,stretch = "lin", ggLayer =T)+
    geom_sf(data = valencia_17, aes(color = Year), show.legend = FALSE,
            size=1.5, shape = 15)+
    scale_color_manual(values=c("midnightblue"))+
    geom_label(data = places_Spain, aes(X, Y, label = name), size = 2.5)+
    theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.line = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill='transparent'),
    plot.background = element_rect(fill='transparent', color=NA)
    ) 

valencia_plot
```

### Wytham


```{r}

wytham <- terra::rast("data/ang20210716t_mosaic_30m_enmap_subset")

wytham_18 <- read.table("data/wytham18_coords.txt",sep="\t",header=T)%>%
  as_tibble()%>%
  st_as_sf(coords = c('Longitude', 'Latitude')) %>%
  st_set_crs(4326)%>%
  st_transform(32630)%>%
  mutate(Year="2018")

wytham_21 <- read.table("data/wytham21_coords.txt",sep="\t",header=T)%>%
  as_tibble()%>%
  st_as_sf(coords = c('Longitude', 'Latitude')) %>%
  st_set_crs(4326)%>%
  st_transform(32630)%>%
    mutate(Year="2021")
  

all<- rbind(wytham_18, wytham_21)


sub_wytham<- subset(wytham, c(9,23,41))%>%
   subst(., 0, NA)%>%
  crop(., all)

wytham_18 <- wytham_18 %>%st_transform(., 3857)
wytham_21 <- wytham_21 %>%st_transform(., 3857)


places_UK <- tibble(name = c("Wytham"), X = c(-146070.6), Y = c(6759433.8))
  # st_as_sf(., coords=c("X", "Y"), crs=4326)%>%
  # st_transform(., 3857)%>%
  # st_coordinates()%>%
  # as_tibble()%>%
  # mutate(name=c("Wytham", "Swinford"))

#layer_scales(wytham_plot)$x$get_limits()


wytham_plot <- ggplot()  +
    basemap_gglayer(all, alpha=0.8)+
    scale_fill_identity() + 
  coord_sf()+
  #ggRGB(sub_wytham, r = 3, g = 2, b = 1,stretch = "lin", ggLayer =T)+
 geom_sf(data = valencia_17, aes(color = Year), show.legend = FALSE,
            size=1.5, shape = 15)+    
  geom_sf(data = wytham_18, aes(color = Year), show.legend = FALSE, 
          size=1.8, shape = 17)+
  geom_sf(data = wytham_21, aes(color = Year), show.legend = TRUE,
            size=0.9, shape = 19)+
    coord_sf(xlim =  c(-150074.6,-145364.1), ylim = c(6756355, 6761285))+
  scale_color_manual(values=c("midnightblue","deepskyblue3","grey24"),
                      guide = guide_legend(override.aes = list(
                                                  shape = c(15, 17,19),
                                                  size = c(1.5, 1.8,0.9))))+
 #   annotation_scale(location = "bl", width_hint = 0.5) +
    geom_label(data = places_UK, aes(X, Y, label = name), size = 2.5)+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.line = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_rect(fill='transparent'),
    plot.background = element_rect(fill='transparent', color=NA),
    legend.title.align=0.5)+ 
  labs(color = "ESU Year")+
  theme(legend.direction="horizontal")

wytham_plot


```

## High resolution imagery

The following code chunks load and plot high resolution imagery for Wytham woods 2021 + 2019 and Valencia 2017. Each image shows a bounding box that indidncates the area from which samples were taken.

### Wytham 2021

```{r}
wytham <- terra::rast("data/ang20210716t_mosaic_30m_enmap_subset")
valencia2b<-terra::rast("data/f168_3b_mapped_utm30n_atm_brdf_mosaic_30m_enmap_subset")



values(wytham)[values(wytham) == 0.00] = NA

places_UK <- tibble(name = c("Wytham"), X = c(-146070.6), Y = c(6759433.8))


places_UK2 <- places_UK %>%
  st_as_sf(.,
          coords = c("X","Y"),
           crs=3857)%>%
  st_transform(., 32630)%>%
  st_coordinates()

places_UK3 <- places_UK%>%
  dplyr::select(name)%>%
  cbind(., places_UK2)

wytham_21_box<- st_as_sfc(st_bbox(wytham_21))%>%
  st_transform(32630)

wytham_raster<- ggRGB(
  wytham,
  r = 38,
  g = 26,
  b = 9,
  limits = NA,
  stretch = "lin")+
 #   geom_label(data = places_UK3, aes(X, Y, label = name), size = 2.5)+
    geom_sf(data=wytham_21_box, fill=NA, color = 'grey24', lwd =1)+
  theme_bw()+
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.line = element_blank(),
        panel.background = element_rect(fill='transparent'),
        plot.background = element_rect(fill='transparent', color=NA),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank())+
    #panel.background = element_blank())+
    annotation_scale(location = "bl",
                     plot_unit="m",
                     pad_x =unit(0.5, "cm"),
                      pad_y=unit(0.6, "cm" ))

  
wytham_raster
```
### Valencia  2017

```{r}
valencia2b<-terra::rast("data/f168_3b_mapped_utm30n_atm_brdf_mosaic_30m_enmap_subset")

values(valencia2b)[values(valencia2b) == 0.00] = NA

places_Spain <- tibble(name = c("Utiel"), X = c(-134164.6), Y = c(4803342.7))

places_Spain2 <- places_Spain %>%
  st_as_sf(.,
          coords = c("X","Y"),
           crs=3857)%>%
  st_transform(., 32630)%>%
  st_coordinates()

places_Spain3 <- places_Spain%>%
  dplyr::select(name)%>%
  cbind(., places_Spain2)

valencia_box<- st_as_sfc(st_bbox(valencia_17))%>%
  st_transform(32630)

valencia_raster<-ggRGB(
  valencia2b,
  r = 38,
  g = 26,
  b = 9,
  limits = NA,
  stretch = "lin")+
  geom_sf(data=valencia_box, fill=NA, color = "midnightblue", lwd =1)+
  #geom_label(data = places_Spain3, aes(X, Y, label = name), size = 2.5)+
  theme_bw()+
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.line = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill='transparent'),
    plot.background = element_rect(fill='transparent', color=NA),
    panel.border = element_blank())+
      annotation_scale(location = "br",
                       plot_unit="m")

valencia_raster
```
### Wytham  2021


```{r}
wytham_21 <- terra::rast("data/f184a013b_mapped_osng_atm_brdf_mosaic_30m_enmap_subset")


values(wytham_21)[values(wytham_21) == 0.00] = NA

crs(wytham_21) <- CRS('+init=EPSG:27700')

places_UK <- tibble(name = c("Wytham"), X = c(-146070.6), Y = c(6759433.8))


places_UK2 <- places_UK %>%
  st_as_sf(.,
          coords = c("X","Y"),
           crs=3857)%>%
  st_transform(., 27700)%>%
  st_coordinates()

places_UK3 <- places_UK%>%
  dplyr::select(name)%>%
  cbind(., places_UK2)

wytham_18_box<- st_as_sfc(st_bbox(wytham_18))%>%
  st_transform(27700)

wytham_raster21<- ggRGB(
  wytham_21,
  r = 38,
  g = 26,
  b = 9,
#  limits = c(100,10000),
 # clipValues=c(100,1000),
  stretch = "lin")+
  geom_sf(data=wytham_18_box, fill=NA, color = 'deepskyblue3', lwd =1)+
  #  geom_label(data = places_UK3, aes(X, Y, label = name), size = 2.5)+
  theme_bw()+
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.line = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
     panel.background = element_rect(fill='transparent'),
    plot.background = element_rect(fill='transparent', color=NA))+
#    panel.background = element_blank())+
    annotation_scale(location = "br",
                    plot_unit="m",
                      pad_x =unit(0.3, "cm"),
                      pad_y=unit(1.25, "cm" ))

 wytham_raster21 
 
```
## Create figure

This figure combines all the the figures above with cowplot.

They are divided into three columns.

  * Left column = high resolution imagery with sampling point extents
  * Middle column = OSM map with sampling points
  * Right column = study area location

The figures are plotted and lines drawn show the relationship between them.

```{r}
legend <- get_legend(
wytham_plot + theme(legend.box.margin = margin(0, 0, 0, 12))+
  theme(legend.key=element_rect(fill="white"))
)


ggdraw(xlim = c(0, 2.5), ylim = c(0, 1), clip = "off") +
  draw_plot(wytham_raster,
            x=0,
           y=0.56,
            height = 0.6,
            width=0.6)+
  draw_plot(wytham_raster21,
            x=0,
            y=0.23,
            height = 0.62,
            width=0.6)+
   draw_plot(valencia_raster,
            x=0,
            y=-0.1,
            height = 0.6,
            width=0.6)+
  draw_plot(valencia_plot,
    height = 0.9,
    width=0.9,
    x = 0.6,
    y = -0.2
  )+
  draw_plot(wytham_plot + theme(legend.position="none"),
    height = 0.9,
    width=0.9,
    x = 0.6,
    y = 0.325
  )+
  draw_plot(legend,
            x=0.53,
            y=0.008)+
  draw_plot(main,
            x=1.505,
            y=0)+
    
  # Valencia OSM to study map
  draw_line(x = c(1.44, 1.71),
    y = c(0.063, 0.495),
    color = "black", size = 0.7, linetype=3, alpha=0.8) +
  draw_line(x = c(1.44, 1.71),
    y = c(0.444, 0.495),
    color = "black", size = 0.7, linetype=3, alpha=0.8)+
  
  # Wytham OSM to study map
  draw_line(x = c(1.44, 1.78),
    y = c(0.58, 0.59),
    color = "black", size = 0.7, linetype=3, alpha=0.8)+
     draw_line(x = c(1.44, 1.78),
    y = c(0.975, 0.59),
    color = "black", size = 0.7, linetype=3, alpha=0.8)+
    
  # Wytham 2021 high imagery to OSM
  draw_line(x = c(0.41, 0.67),
    y = c(0.565, 0.58),
    color = "deepskyblue3", size = .9, linetype=3)+
  
  # Wytham 2018 high imagery to OSM
  draw_line(x = c(0.43, 0.67),
    y = c(0.950, 0.975),
    color = "grey24", size = .9, linetype=3)+
   
  # Valencia 2017 high imagery to OSM
  draw_line(x = c(0.42, 0.67),
    y = c(0.28, 0.441),
    color = "midnightblue", size = .9, linetype=3)+
   draw_line(x = c(0.42, 0.67),
    y = c(0.13, 0.061),
    color = "midnightblue", size = .9, linetype=3)+
  draw_text("Map data from OpenStreetMap", x = 0.3, y = 0.03, size = 8)


ggsave("study_area.png", width = 20, height = 16, units = "cm", bg="white",   dpi = 400)

```
